Calculating life expectancy and exploring missingness

### 2016-09-30 Code/1_Explore_Data_v2.Rmd
more plots added to the app

@@

```{r}
save(dat.clean, dat2, file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

make a new dataset that contains information on the gap

```{r}
Black <- dat2 %>% filter(Race2 == "Black" & Age3 == 0) %>% 
                  select(State2, Year3, Sex2, Pop_across_age, life.expectancy.birth) %>%
                  rename(Pop_black = Pop_across_age,  le.birth.black = life.expectancy.birth)

White <- dat2 %>% filter(Race2 == "White" & Age3 == 0) %>% 
                  select(State2, Year3, Sex2, Pop_across_age, life.expectancy.birth) %>%
                  rename(Pop_white = Pop_across_age,  le.birth.white = life.expectancy.birth)

BlackWhite <- merge(Black, White, by = c("State2", "Year3", "Sex2"))

BlackWhite <- BlackWhite %>% mutate(WBgap = le.birth.white - le.birth.black)

@@

```{r}
save(dat.clean, dat2, BlackWhite, file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```
